\documentclass[a4paper,11pt]{article}

% Package imports
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{cfr-lm}
\usepackage[T1]{fontenc}
\usepackage{fontawesome5}

% Color definitions
\definecolor{darkblue}{RGB}{0,0,139}

% Page layout
\setlength{\multicolsep}{0pt} 
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\geometry{left=1.4cm, top=0.8cm, right=1.2cm, bottom=1cm}
\setlength{\footskip}{5pt} % Addressing fancyhdr warning

% Hyperlink setup (moved after fancyhdr to address warning)
\usepackage[hidelinks]{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=darkblue,
    filecolor=darkblue,
    urlcolor=darkblue,
}

% Custom box settings
\usepackage[most]{tcolorbox}
\tcbset{
    frame code={},
    center title,
    left=0pt,
    right=0pt,
    top=0pt,
    bottom=0pt,
    colback=gray!20,
    colframe=white,
    width=\dimexpr\textwidth\relax,
    enlarge left by=-2mm,
    boxsep=4pt,
    arc=0pt,outer arc=0pt,
}

% URL style
\urlstyle{same}

% Text alignment
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

% Custom commands
\newcommand{\resumeItem}[2]{
  \item{
    \textbf{#1}{\hspace{0.5mm}#2 \vspace{-0.5mm}}
  }
}

\newcommand{\resumePOR}[3]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1}\hspace{0.3mm}#2 & \textit{\small{#3}} 
    \end{tabular*}
    \vspace{-2mm}
}

\newcommand{\resumeSubheading}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#4}} \\
        \textit{\footnotesize{#3}} &  \footnotesize{#2}\\
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeProject}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#3}} \\
        \footnotesize{\textit{#2}} & \footnotesize{#4}
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand{\labelitemii}{$\vcenter{\hbox{\tiny$\circ$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=1mm]}
\newcommand{\resumeHeadingSkillStart}{\begin{itemize}[leftmargin=*,itemsep=1.7mm, rightmargin=2ex]}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*,labelsep=1mm,itemsep=0.5mm]}

\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{2mm}}
\newcommand{\resumeHeadingSkillEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\cvsection}[1]{%
\vspace{2mm}
\begin{tcolorbox}
    \textbf{\large #1}
\end{tcolorbox}
    \vspace{-4mm}
}

\newcolumntype{L}{>{\raggedright\arraybackslash}X}%
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}%
\newcolumntype{C}{>{\centering\arraybackslash}X}%

% Commands for icon sizing and positioning
\newcommand{\socialicon}[1]{\raisebox{-0.05em}{\resizebox{!}{1em}{#1}}}
\newcommand{\ieeeicon}[1]{\raisebox{-0.3em}{\resizebox{!}{1.3em}{#1}}}

% Font options
\newcommand{\headerfonti}{\fontfamily{phv}\selectfont} % Helvetica-like (similar to Arial/Calibri)
\newcommand{\headerfontii}{\fontfamily{ptm}\selectfont} % Times-like (similar to Times New Roman)
\newcommand{\headerfontiii}{\fontfamily{ppl}\selectfont} % Palatino (elegant serif)
\newcommand{\headerfontiv}{\fontfamily{pbk}\selectfont} % Bookman (readable serif)
\newcommand{\headerfontv}{\fontfamily{pag}\selectfont} % Avant Garde-like (similar to Trebuchet MS)
\newcommand{\headerfontvi}{\fontfamily{cmss}\selectfont} % Computer Modern Sans Serif
\newcommand{\headerfontvii}{\fontfamily{qhv}\selectfont} % Quasi-Helvetica (another Arial/Calibri alternative)
\newcommand{\headerfontviii}{\fontfamily{qpl}\selectfont} % Quasi-Palatino (another elegant serif option)
\newcommand{\headerfontix}{\fontfamily{qtm}\selectfont} % Quasi-Times (another Times New Roman alternative)
\newcommand{\headerfontx}{\fontfamily{bch}\selectfont} % Charter (clean serif font)

\begin{document}
\headerfontiii

% Header
\begin{center}
    {\Huge\textbf{GAUTHAM R}}
\end{center}
\vspace{-6mm}

\begin{center}
    \small{
    +91 9042398270 | \href{mailto:gauthamramesh93442@gmail.com}{gauthamramesh93442@gmail.com} | 
    \href{https://personal-portfolio-two-sooty.vercel.app/}{personal-portfolio-two-sooty.vercel.app}
    }
\end{center}
\vspace{-6mm}

\begin{center}
    \small{
    \socialicon{\faLinkedin} \href{https://www.linkedin.com/in/gauthamramesh07/}{LinkedIn} | 
    \socialicon{\faGithub} \href{https://github.com/rgautham7}{Github}
    }
\end{center}
\vspace{-6mm}
\begin{center}
    \small{Chennai, India}
\end{center}

\vspace{-4mm}

\section{\textbf{Objective}}
\vspace{1mm}
\small{
Driven Full stack professional with more than 250 Leetcode resolves, fueled by a passion for innovation and growth. Seeking to harness deep technical expertise and results-oriented mindset to build impactful solutions that push the boundaries of online experiences. Eager to collaborate seamlessly and translate complex challenges into elegant cloud-powered architecture. With strong experience in team building and problem-solving, I seamlessly integrate into any team, contributing to its growth while consistently striving for excellence and delivering high-quality results.
}
\vspace{-2mm}



\section{\textbf{Experience}}
\vspace{-0.4mm}
  \resumeSubHeadingListStart
  \resumeSubheading
      {{Octanet}}{Chennai, India}
      {VIRTUAL WEBDEV INTERN}{Sept 2024 - Oct 2024}
      \resumeItemListStart
      \item Developed and deployed real-world projects addressing social causes.
      \item Built a Todolist application with AI integration, elevating customer usage time by 45\%.
      \item Explored new technologies and component libraries for the project.
      \resumeItemListEnd 
  \resumeSubHeadingListEnd
\vspace{-6mm}


\section{\textbf{Education}}
\vspace{-0.4mm}
\resumeSubHeadingListStart

\resumeSubheading
{Vellore Institute of Technology, Chennai}{Chennai}
{B. Tech - Computer Science and Engineering}{Sept 2021 - July 2025}
\resumeItemListStart
\item GPA: 8.37/10
\resumeItemListEnd

\resumeSubheading
{PCKG Govt. Hr. Sec. School}{Chennai}
{Higher Secondary Schooling - 12th grade}{June 2021}
\resumeItemListStart
\item Grade: 92.5\%
\resumeItemListEnd

\resumeSubheading
{PCKG Govt. Hr. Sec. School}{Chennai}
{Secondary Schooling - 10th grade}{June 2019}
\resumeItemListStart
\item Grade: 92\%
\resumeItemListEnd

% \resumeSubheading
% {High School Name}{City, Country}
% {Secondary Education}{Month Year}
% \resumeItemListStart
% \item GPA: X.X/10
% \resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-6mm}

\section{\textbf{Projects}}
\vspace{-0.4mm}
\resumeSubHeadingListStart

\resumeProject
{BlogApp\_Express: Full-Stack Web Application}
{Tools: Node.js, Express.js, MongoDB}
{August 2024}
{{}[\href{https://github.com/rgautham7/BlogApp_Express}{\textcolor{darkblue}{\faGithub}}]}
\resumeItemListStart
  \item Designed a full-stack web application (BlogApp\_Express) integrating a server-side application (Node.js \& Express.js) with a NoSQL database (MongoDB) for dynamic content management.
  \item Implemented CRUD operations (Create, Read, Update, Delete) for efficient blog post management, reducing blog management time by 25\%.
  \item Developed a user-friendly interface for creating blog posts (title, snippet, body), displaying all posts, viewing single posts, and deleting posts.
\resumeItemListEnd

\resumeProject
{Plate Perfect: Personalized Meal Planning App}
{Tools: Next.Js, Shadcn, Tailwind CSS}
{October 2024}
{{}[\href{https://github.com/rgautham7/Meal_planner}{\textcolor{darkblue}{\faGithub}}]}

\resumeItemListStart
  \item Developed a personalized meal planning app using Next.js along with ShadCN components and Tailwind CSS for efficient development and a visually appealing user interface.
  \item Implemented features like personalized meal plan generation, grocery list creation, and dietary preference filtering.
  \item Achieved a 24\% reduction in meal planning time and an 18\% increase in user satisfaction through automated meal plans and personalized recommendations.
\resumeItemListEnd

% \resumeProject
%   {Project B: [Brief Description]}
%   {Tools: [List of tools and technologies used]}
%   {Month Year}
%   {{}[\href{https://github.com/your-username/project-b}{\textcolor{darkblue}{\faGithub}}]}
% \resumeItemListStart
%   \item Developed [specific model/system], achieving [specific metric]
%   \item Implemented [specific feature], processing [specific volume] of data
%   \item Created [specific visualization] for [specific purpose]
%   \item Developed [specific component] for easy integration with [specific system]
% \resumeItemListEnd

\resumeSubHeadingListEnd

\section{\textbf{Skills}}
\vspace{-0.4mm}
 \resumeHeadingSkillStart
  \resumeSubItem{Programming Languages:}
    {Java, Javascript, C++, Python}
  \resumeSubItem{Web Technologies:}
    {Data Structures, Cloud services, Operating Systems, Database Management System}
  \resumeSubItem{Web Technologies:}
    {React, NextJS, Github}
  \resumeSubItem{Database Systems:}
    {MySQL, Postgresql, MongoDB}
  \resumeSubItem{Cloud Technologies:}
    {AWS, GCP}
  \resumeSubItem{Design:}
    {UI/UX, Prototyping, Figma, Canva, Notion}
 \resumeHeadingSkillEnd

\section{\textbf{Honors and Awards}}
\vspace{-0.4mm}
\resumeSubHeadingListStart

\resumeProject
  {STARS}
  {Vellore Institute of Technology, Chennai}
  {July 2021}
  
\resumeItemListStart
  \item Secured full fee-waiver scholarship under the scheme of STARS for government school students, securing School first in 12th grade.
\resumeItemListEnd

% \resumeProject
%   {Award Name B}
%   {Awarding Institution/Organization}
%   {Month Year}
%   {{}[\href{https://award-link-b.com}{\textcolor{darkblue}{\faIcon{globe}}}]}
% \resumeItemListStart
%   \item Brief description of the award and its significance
%   \item Impact or recognition associated with the award
% \resumeItemListEnd

\resumeSubHeadingListEnd

\vspace{-6mm}
\section{\textbf{Leadership Experience}}
\vspace{-0.4mm}
\resumeSubHeadingListStart
\resumeProject
{DIRECTOR OF COMMUNITY WELFARE} 
{The Mind Palace}
{Sept 2024 - Present}

\resumeItemListStart
  \item Volunteered for community improvement, focusing on mental health.
  \item Organized events and led workshops on work culture and work-life balance.
\resumeItemListEnd

\resumeSubHeadingListEnd

\vspace{-6mm}

\section{\textbf{Certifications}}
\vspace{-0.2mm}
\resumeSubHeadingListStart
\resumePOR{}{\href{https://drive.google.com/file/d/121d5xo8C071seyQ2VOFSZjqbtybwMNWl/view?usp=sharing}{
\textbf{ADOBE UI/UX (GRAPHIC DESIGNER)}
}}{August 2024}
\resumePOR{}{\href{https://drive.google.com/file/d/18b3OW6OE-zSmf2eAOok4goqv9MbNO6qg/view?usp=sharing}{
\textbf{THE COMPLETE WEB DEVELOPMENT BOOTCAMP}
}}{August 2024}
\resumePOR{}{\href{https://drive.google.com/file/d/1s5d54iozT3NOT9_q0xEu3fKZHe6G3u1L/view?usp=sharing}{
\textbf{CLOUD PRACTITIONER}
}}{January 2024}
\resumePOR{}{\href{https://drive.google.com/file/d/1MxXjV2IWbiH_S7XgOcUNM5N8dsAU2Xpz/view?usp=sharing}{
\textbf{CLOUD DIGITAL LEADER}
}}{December 2023}
\resumeSubHeadingListEnd
\vspace{-6mm}

% \section{\textbf{Additional Information}}
% \vspace{-0.4mm}
% \small{
% \textbf{Languages:} Language A (Proficiency level), Language B (Proficiency level), Language C (Proficiency level)

% \textbf{Interests:} Interest 1, Interest 2, Interest 3, Interest 4
% }
% \vspace{-4mm}

\end{document}